---
title: "R Notebook"
output: html_notebook
---


```{r}

library(tidyverse)
library(janitor)
library(infer)

```


```{r}

ames <- read_csv("data/ames.csv")
ames <- clean_names(ames)

glimpse(ames)

```


 Plot a histogram of sale_price. Is the distribution normal?
 
```{r}

ames %>%
  ggplot(aes(x = sale_price)) +
  geom_histogram(col = "white", bins = 30)

```

sale price looks as though it has some right skew


Calculate the population parameter mean of sale_price. Store it in a variable, as we’ll need this value later when we check if each CI contains the parameter value or not.


```{r}
mean_sale_price <- ames %>%
  summarise(
    mean_sale_price = mean(sale_price)
  ) 

mean_sale_price

```


```{r}

results <- tibble()
for (sample_num in 1:1000){

  # get a new 100-observation random sample from ames
  this_sample <- ames %>%
    rep_sample_n(size = 100, reps = 1) %>%
    ungroup() %>%
    select(sale_price)
  
  #bootstrap distribution of mean(sale_price) 1000 reps
 
    this_bootstrap <- this_sample %>%
    specify(response = sale_price) %>%
    generate(reps = 1000, type = "bootstrap") %>%
    calculate(stat = "mean")

  # get 95% CI for this bootstrap distribution
  this_ci <- this_bootstrap %>%
    get_ci(level = 0.95, type = "percentile")
  
  # prepare new row for results, storing CI bounds
  this_result <- c(
    sample_num = sample_num, 
    lower = this_ci[[1]], 
    upper = this_ci[[2]]
  )
  
  # add this_result to growing tibble of results
  results <- bind_rows(results, this_result)
}

results


```


Pipe results to mutate() to add a new variable popn_param_in_ci which will be TRUE if the population parameter we calculated earlier is between lower and upper, and FALSE otherwise

```{r}

results %>%
  mutate(popn_param_in_ci = TRUE < lower | TRUE < upper)

```

Perform an appropriate summarise() to determine the proportion of CIs that contain the population parameter. Our confidence level was 95%. Is your proportion close to that value.


```{r}

results%>%
  summarise(
    mean = mean(sale_price),
    lower_bound = quantile(mean_sale_price, probs = 0.025),
    upper_bound = quantile(mean_sale_price, probs = 0.975)
  )

```


































