---
title: "R Notebook"
output: html_notebook
---

```{r}

library(readr)
library(tidyverse)
library(dplyr)
library(stringr)

```


Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names

```{r}

code_clan_tweets <- read_csv("data/code_clan_tweets.csv")

```

```{r}

dim(code_clan_tweets)


```

```{r}

names(code_clan_tweets)

```

Q2. First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.


```{r}

favorite_count_tweet <- summary(code_clan_tweets$favorite_count)

favorite_count
```




```{r}
ggplot(code_clan_tweets, aes(x = "favorite_count", favorite_count)) + 
  geom_boxplot()

```




3. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}

code_clan_tweets %>%
  filter(is_quote == FALSE) %>%
  summarise(total = sum(favorite_count))
  


```




Q4.  Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.


```{r}

code_clan_tweets %>%
  filter(is_quote == FALSE) %>%
  group_by(source) %>%
  summarise(average_retweet = mean(retweet_count))

```



Q5.

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.



```{r}

code_clan_tweets %>%
  mutate(media_type2 = replace_na(media_type, "text")) %>%
  group_by(media_type2) %>%
  summarise(favourite_count_total = sum(favorite_count)) %>%
  arrange(desc(favourite_count_total))

```





Q6. Find the mean number of characters that a CodeClan tweet contains.

```{r}

code_clan_tweets %>%
  summarise(avg_tweet_lenght = mean(display_text_width))
  
  

```



Q7. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.


```{r}

code_clan_info <- read_csv("data/code_clan_info.csv")

```


```{r}

names(code_clan_info)


```

```{r}

codeclan_all <- left_join(code_clan_tweets,code_clan_info, by = "tweet_id")

```




```{r}
# 8 : create a variable which has all the hashtags in lowercase for analysis


codeclan_hashtags <- codeclan_all%>% 
  select(tweet_id, hashtags) %>%
  mutate(lowcase_hashtag = str_to_lower(hashtags)) %>%
  select(-hashtags) %>%
  drop_na(lowcase_hashtag)

codeclan_hashtags


```



































































