---
title: "R Notebook"
output: html_notebook
---


```{r}

library(tidyverse)


```
Question 1
Let’s start by loading the tidyverse library and reading the data in. Find out the dimenions, variable names, and print the first 10 rows. 

```{r}

facial_recognition <- read_csv("data/face_descriptions.csv")

dim(facial_recognition)

```



```{r}

head(facial_recognition, 10)


```

Question 2

Do these variable names look tidy to you? What format is your data in (long or wide)?

No data is not organised and has lot of variations. 



Question 3
Being faced with such complex data can be daunting, we may feel overwhelmed and ask ourselves:

How can I organise this data?
How can I make this data meaningful?
How can I make this data tidy?
The first problem you can always tackle is to get your data in an appropriate format. What format do you need?

Once you have figured that out, reshape the data into the appropriate format.


A. 

```{r}

facial_recognition <-
facial_recognition %>%
  pivot_longer(
    cols = starts_with("t"),
    names_to = "face_id",
    values_to = "Description"
  )

```

Question 4

First, you’ll need to decide a cut off for how many responses you want to accept from people. Is one enough? Two? Three? Once you’ve decided how many descriptions you want to code, you’ll have to separate your description columns into that many columns.


```{r}
facial_recognition <-
facial_recognition %>%
  separate(
    col = Description,
    into = c("d1", "d2", "d3"),
    sep = "/"
  )

```

Question 5

What do we need to do here so our description variables follow the rules of tidy data?

```{r}

all_description <-
  
facial_recognition %>%
  pivot_longer(
    cols = d1:d3,
    names_to = "description_number",
    values_to = "description"
  
  )


```



Question 6

But, wait… another problem arises… not everyone provided three descriptions! So, if you look at the data, we have some missing values (NAs). We also have some nonsense descriptions (e.g. “f” and “.”). Let’s now sort these out.

Use the filter function to get rid of NA’s and useless descriptions. 


```{r}
all_description <-

all_description %>%
  
 filter(!is.na(description),
         nchar(description) > 1)

all_description

```


Question 7

Now we can actually find something out about our data. Let’s find out what the most common description of each face is. Earlier in the week you learnt how to pipe functions together to create summary stats.

Group the data by description, and summarise the data by generating a count for each group.




```{r}

# group the data
all_description <-
  
all_description %>%
  group_by(description)
head(all_description)

# summarise and generate a count for each 
summarise_data <- summarise(all_description, n = n())

summarise_data

```


Question 8

Finally, arrange the output so that we have the most common description at the top, and the least common at the bottom.
Hint: do you need ascending or descending order for this?
Create a tibble called top_10_descriptions, which filters your arranged data so that it only takes the top 10 answers.

This will help us answer the question: what are the most common descriptions of faces given?


```{r}




```
















































