---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
library(feasts)

```



Load in the nyc_bikes data from the tsibbledata package. 

```{r}
nyc_bikes <- nyc_bikes

names(nyc_bikes)  
dim(nyc_bikes)
head(nyc_bikes,3)

```




```{r}
nyc_bikes_year <-
nyc_bikes %>%
  select(-gender, -type, -birth_year) %>%
  mutate(year = year  (start_time),
         month = month(start_time, label = TRUE),
         date  = date(start_time))


```


Summarise the number of bike hire counts by month. Make a plot of this data. 

```{r}

nyc_bikes_month <-
nyc_bikes_year %>%
index_by(month) %>%
  summarise(count = n())


  ggplot(nyc_bikes_month) +
  aes(x = month, y = count) +
  geom_point() + 
  geom_line(group = 1) +              
  ggtitle("Bike hire in NYC") + 
  xlab("Month") + ylab ("total count")
  

```



Summarise the number of bike hire counts by date. Make a plot of this new aggregated data. 

```{r}

nyc_bikes_date <-
nyc_bikes_year %>%
index_by(date) %>%
  summarise(count = n())


    ggplot(nyc_bikes_date) +
  aes(x = date, y = count) +
  geom_point() + 
  geom_line(group = 1) +              
  ggtitle("Bike hire in NYC") + 
  xlab("Month") + ylab ("total count")




```


build a model. For this, we will use the downsampled by date dataset we created above.

```{r}
# fill the gaps with median

nyc_bikes_filled <- nyc_bikes_date %>%
  fill_gaps(count = as.integer(median(count)))

nyc_bikes_filled

```

```{r}

fit <- nyc_bikes_filled %>%
  model(
    snaive = SNAIVE(count),
    mean_model = MEAN(count),
    arima = ARIMA(count)
  )

fit

```


Forecasting to predict bike use over the next four months bu using model fit above. Plot your models alongside your data.


```{r}

forecast_bike_use <- fit %>%
  fabletools::forecast(h = 120)

forecast_bike_use



forecast_bike_use %>%
  autoplot(nyc_bikes_filled, level = NULL) +
  ggtitle("Forecasts for bikes usage") +
  xlab("month") +
  guides(colour = guide_legend(title = "Forecast"))
  

```



```{r}

# create a shorter interval to plot: years after 1980
bikes_shorter <- nyc_bikes_filled %>%
  mutate(month = month(date)) %>%
  filter(month >= 8)

# check one model at a time
forecast_bike_use %>%
  filter(.model == "snaive") %>%
  autoplot(bikes_shorter, level = NULL)


```



model accuracy test, build a forecast on the training set, and then plot the training set forecast against the real data. Calculate model accuracy.


```{r}

# Set training data from Jan to Nov

train <- nyc_bikes_filled %>%
  mutate(month = month(date)) %>%
  filter(month <= 10) 


# run the model on the training set 
bikes_fit_test <- train %>%
  model(
    mean_model = MEAN(count),
    arima = ARIMA(count),
    snaive = SNAIVE(count))

bikes_fit_test

```


```{r}

# forecast from the training set
forecast_bike_use <- bikes_fit_test %>%
  fabletools::forecast(h = 12*6)

# Plot forecasts against actual values
forecast_bike_use %>%
  autoplot(train, level = NULL) +
    autolayer(nyc_bikes_filled, color = "black")

```


Question 7

Look at your forecast plots and accuracy values. Describe your results. Are your models a good fit for the data? If not, why not? What would you suggest doing with the data if you were expected to present these back to a client? For example, would you ask for more data? Would you test a different model?




orecast isn’t great. This could be for several reasons:

    not enough data
    something is affecting it
    wrong model choice

I’d collect more data if possible - we only have a year’s worth so far.


ggplot (geom_point) which plots the start longitude and latitudes of each bike and facet for each bike_id. 


```{r}

library(ggplot2)

# make the month 
nyc_bikes_spatial <- nyc_bikes %>%
  select(bike_id, start_time, start_lat, start_long, end_lat, end_long) %>%
  mutate(month = month(start_time, label = TRUE))

# make a faceted plot : start points
ggplot(nyc_bikes_spatial) + 
  geom_point(aes(x=start_lat, y = start_long, colour = month)) +
  facet_wrap(~bike_id) +
  ggtitle("NYC bikes: start points") +
  xlab("Latitude") + ylab("Longitude")

```




```{r}
# a faceted plot : end points

ggplot(nyc_bikes_spatial) + 
  geom_point(aes(x=end_lat, y = end_long, colour = month)) +
  facet_wrap(~bike_id) +
  ggtitle("NYC bikes : end points") +
  xlab("Latitude") + ylab("Longitude")

```




```{r}
# a leaflet plot
library(leaflet)

# leaflet map
leaflet(nyc_bikes_spatial) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~start_long,
                   lat = ~start_lat) %>%
    setView(-74.00, 40.71, zoom = 12) %>%
  addProviderTiles("CartoDB.Positron")

```



































