---
title: "Reading in data - homework"
output: html_notebook
---

1.1 Read in the state_income_data.csv file using the appropriate function


```{r}


income <- read.csv("data/state_income_data.csv")


```

1.2 How do you specify your own column names when using read_csv()

colnames = 


1.3 Read in the cars.csv file and use the col_types() function to ensure you load in:

X1 as character, mpg, cyl, disp, hp as double, vs as logical

```{r}


cars_data <- read_csv("data/cars.csv", col_types = cols(
  
    X1 = col_character(), 
    mpg = col_double(),
    cyl = col_double(),
    disp = col_double(),
    hp = col_double(),
    vs = col_logical()
    
    ))


```


Read in the scotland.txt file using the appropriate function.

```{r}

Scotland <- read_delim("data/scotland.txt", delim = ";")

```

```{r}

# How do you read text into a one element character vector?

read_file

```

 6.  Read in the steam-200k-sample.csv file. Fix any problems you may encounter.

```{r}

games_data <- read_csv("data/steam-200k-sample.csv", skip = 4)


```

Read in the historic_eu_payments.tsv file.

```{r}

EU_payments <- read_tsv("data/historic_eu_payments.tsv")


```

How do you read lines of text into a multi-element text vector?

```{r}

read_lines()

```

Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt

```{r}
library("rjson")

Json_data <- fromJSON(file = "http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")


```

2 Extension
A lot of Excel sheets you will encounter will contain more than one sheet. Try to write some code that reads in all the different sheets in the file green_bindle_consulting.xlsx.

[ you will need to write a for loop]

```{r}

library(readxl)

green_excelsheets <- length(excel_sheets("data/green_bindle_consulting.xlsx"))

  for(x in 1:green_excelsheets) { 
    assign(paste0("data_sheet

 
 }

```

  





























