---
title: "R Notebook"
output: html_notebook
---



```{r}

library(tidyverse)
library(infer)
library(janitor)


```


```{r}

data("msleep")

```

Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

```{r}

total_sleep <- msleep %>%
  summarise(
    mean_sleep_total = mean(sleep_total)
  )

total_sleep

```

```{r}

mean_sleep <- msleep %>%
  rep_sample_n(size = 50, reps = 1) %>%
  ungroup() %>%
  summarise(
    mean_sleep_total = mean(sleep_total)
  )

mean_sleep

```

From the above statistical test, we can significant difference between the mean of total sleep and sleeping hours of jabberwockies


```{r}

unique(msleep$vore)

```

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

```{r}


```



Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%. 

```{r}

is_domesticated <- msleep %>%
  mutate(conservation = ifelse(conservation == "domesticated", "domesticated", "not_domesticated"))

```


```{r}

null_distribution <- is_domesticated %>%
  filter(!is.na(conservation)) %>%
  specify(response = conservation, success = "domesticated") %>% 
  hypothesize(null = "point", p = 0.05) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop") 

head(null_distribution) 

```


1.2 Hypothesis testing - interpretation
1.2.1 Defining the Hypothesis

1. Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07

Since our p-value 0.07 is greater than α=0.05 we fail to reject H0. There is not enough evidence to say that marketing advertisement have significantly increase the awarness.The p-value approached the borderline of significance.


2. Website company problem. Significance level: 0.01, p-value: 0.006




























