---
title: "Wresteling databses"
output: html_notebook
---


Create a local PostgreSQL database called wrestling


Seed the wrestling database from the file wrestling.sql using the psql PostgreSQL command line interface.


Create a connection to the local wrestling database from R.
Don’t forget to lock all the keychains you use.
Pass the argument max.con = 2 to PostgreSQL() to make sure you don’t have too many simultaneous connections. 
Remember to add a separate ‘disconnect’ block of code. We’ll write queries between the ‘connect’ and ‘disconnect’ blocks.


Using the R connection you just created, write and execute a SQL query to return all the wrestlers in the wrestlers table.


Explore the columns stored in the table. State which data type you think each column stores.

```{r}

library(keyring)
library(RPostgreSQL)

keyring_unlock("local")
username <- key_get("postgresql_username", keyring = "local") 
password <- key_get("postgresql_password", keyring = "local")
keyring_lock("local")

```


```{r}

my_db_connection <- dbConnect(drv = PostgreSQL(), user = username, password = password, dbname = "wrestling", host = "localhost")

```

```{r}


dbListTables(conn = my_db_connection)

```

```{r}

dbListFields(conn = my_db_connection, name = "wrestlers")
```

```{r}

data <- dbGetQuery(conn = my_db_connection, statement = "SELECT * FROM wrestlers")

```




```{r}

dbGetQuery(conn = my_db_connection, statement = "SELECT * FROM wrestlers = 'name,")


```






```{r}


dbDisconnect(conn = my_db_connection)
```


1.2 Remote PostgreSQL connections













