---
title: "Day_5 Homework"
output: html_notebook
---

2 MVP

2.2 if statements and functions


2.2.1
Write a function which multiples all numbers by 15 and adds 4.

Input	Output
1	19   289
2	34   514
3	49   739 

```{r}

fifteen_times_add4 <- function(x) {
  
  return(x * 15 + 4)
  
  }

fifteen_times_add4(49)


```

```{r}
make_table(fifteen_times_add4, c(19, 34, 49))

```


2.2.2

Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.


Input	     Output
goose	     bird
apple	     not bird
5	not      bird
seagull	   not bird

```{r}

Birds_or_not_birds <- function(x) {
  
if ( x %in% c("goose", "duck", "pigeon")) {
  
  return("bird") }
  
     else { 
       
       return("not bird")}
}


```

```{r}

make_table(Birds_not_bird, c("goose", "duck", "pigeon", "dog", "cat"))
```





2.2.3

Write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”.

Input	              Output
2	                  20
5.3	                53
x	                  Invalid input
7	                  70



```{r}

numbers_times_10 <- function(x) {
  
  if (is.numeric(x)) {
     
  return(x * 10) 
    
    } else { 
     
     return("Invalid input")}

}

numbers_times_10("x")

```

```{r}
make_table(numbers_times_10, list(2, 5.3, "x", 7L, "y", "z", 9, 80))
```


2.3 ifelse(), recode() and case_when()

No if or loops

ifelse(), recode() or case_when().

Remember to load dplyr to use recode() and case_when().

2.3.1
For the vector below, make a new vector which is equal to “Big” every time the element of sizes is greater than 10, and equal to “Small” every time the element of sizes is less than or equal to 10.

```{r}
library(dplyr)
```


```{r}
sizes <- c(13, 15, 10, 8, 22)

#ifelse

ifelse(sizes > 10, "Big", "Small")


sizes
```


2.3.2
For the vector below convert:

apple → alpaca

banana → bonobo

cherry → chipmunk

```{r}

fruit <- c("apple", "apple", "banana", "cherry", "cherry")


```

```{r}

case_when( 
          fruit ==  "apple" ~ "alpaca",
          fruit ==  "banana" ~ "bonobo",
          fruit ==  "cherry" ~ "chipmunk"
          )

```

```{r}

recode(fruit, apple = "alpaca", banana = "bonobo", cherry = "chipmunk")

```

2.3.3
The two vectors below show the ages at marriage of each member of a couple. The first elements of each vector correspond to the first couple, the second elements to the second couple, and so on.

Create a new vector which is equal to:

“Wife older” whenever the wife’s age is highest “Husband older” when the husband’s age is highest “Same age” when they are the same age

```{r}

wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)

```


```{r}

case_when(
         wife_age > husband_age ~ "wife older",
         husband_age > wife_age ~ "husband older",
         wife_age ==  husband_age ~ "Same age"
  )

```
```{r}

ifelse(wife_age > husband_age, "wife older", ifelse(husband_age > wife_age, "husband older", "Same age"))  


```

2.4 Loops


```{r}

my_list <- list(4, "apple", 10.5, c("is", "an", "apple"),
  "apple", c("i", "like", "apples"),
  8
)

```


# Use a loop to print out every element of my_list which is of type character. Decide if you need a for loop or a while loop.

```{r}

for (element in my_list) {
  
  if (is.character(element)) {
    print(element)
  }
  
}

```

```{r}

for (element in my_list) {
  
  if (is.character(element)) {
    
    if ( length(element) > 1 ) {
      
    print(paste(element, collapse = " "))
      
  } else {
    
    print(element) 
    
  }
  
}

}

```




```{r}

for (x in my_list) {
  
  if (is.numeric(x)) {
    print(x)
  }
  
}


```

























