---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(janitor)
library(dplyr)

# visualisation packages
library(ggiraphExtra)
library(GGally)

```

```{r}
 avocado <- read_csv("data/avocado.csv")
 data_dic <- read_csv("data/data_dict.txt")

head(avocado)

```


```{r}
glimpse(avocado)

```




```{r}
avocado_tidy <- avocado %>%
  select(-Date, - region) %>%
  mutate(type = as.factor(type)) %>%
  rename(total_volume = 3, plu_4046 = 4, plu_4225 = 5, plu_4770 = 6)


glimpse(avocado_tidy)
```



First predictor

Now, our aim is to build a regression model for the avocado response variable in terms of the multiple potential predictors held in the data frame. Let’s have a look at the associations of the predictors with prestige and with each other.

We wnt to build an explanatory model

```{r}

avocado_tidy %>%
  ggpairs(aes(color = type, alpha = 0.5))
  

```


Now comes the manual model building part. Let’s build seperate models and choose between them on the basis of r2

and diagnostics.

Let’s start with average price

```{r}
# build a model which tries to predict average price from total volume

mod1a <- lm(formula = AveragePrice ~ total_volume, data = avocado_tidy)
mod1a

```
This equation tells us that the predicted averageprice will vary decrease by 0.00000002  for every one unit increase in totalvolume.

We can then use the summary function to provide more information:

```{r}
summary(mod1a)

```

So, what does this tell us?

It tells us that our r2
value is really low (0.037) and so we can explain on 3% of the variance.So that’s not the most perfect prediction out there.


```{r}

# set our plotting parameter limits (2x2 graph)
par(mfrow = c(2, 2)) 

# plot
plot(mod1a)

```
Our residuals vs fitted plot seems to capture the systematic variation well, and the normal Q-Q plot shows a little deviation from normality. Nothing too major here.

```{r}
#type

model1b <- lm(formula = AveragePrice ~ type, data = avocado_tidy)

 summary(model1b)

```

model1b shows higher r-squared value around 37% significantly higher than first predictor

```{r}

par(mfrow = c(2, 2))

plot(model1b)
```

adding more predictors


```{r}

model2a <- lm(formula = lm(formula = AveragePrice ~ type + plu_4225 + plu_4770, data = avocado_tidy))

summary(model2a)

```

R-squared value is 38% which is only 1% higher than type predictor 

lets include year as well 

```{r}
model2b <- lm(formula = lm(formula = AveragePrice ~ type + plu_4225 + plu_4770 + year, data = avocado_tidy))

summary(model2b)

```




















