---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(modelr)
library(broom)

```


```{r}
plot(lm(dist~speed,data=cars)) 

```

2 project_management analysis

```{r}

prject_manag_data <- read_csv("data/project_management.csv")

```



Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.


```{r}

prject_manag_data %>%
  ggplot(aes(x = estimated_length, y = actual_length))+
  geom_point()

```

Label the data points with their row number in the data frame using geom_text() [Hint - you can pass aes(label = 1:nrow(project)) to this layer to generate row index labels]

Identify by eye any points you think might be outliers and note their labels.

Further split your outliers into those you think are ‘influential’ or ‘non-influential’ based on a visual assessment of their leverage.


```{r}


plot <- prject_manag_data %>%
  ggplot(aes(x = estimated_length, y = actual_length))+
  geom_text(aes(label = 1:nrow(prject_manag_data)))+
  geom_point()

plot


```




```{r}

plot(lm(estimated_length ~ actual_length, data = prject_manag_data))

```





























