---
title: "R Notebook"
output: html_notebook
---


```{r}
library(prob)
library(tidyverse)

```

Q1. If I roll a six-sided dice once, what is the probability of getting a number less than 5

```{r}
one_dice <- rolldie(1)

less_than_5 <- one_dice %>%
  filter(X1 < 5)

# calculate the probability of less than 5
prob_less_than_5 <- nrow(less_than_5) / nrow(one_dice)

prob_less_than_5


```

Q2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}

three_dice <- rolldie(3)

# the sample space
three_dice %>%
summarise(size_of_s = n())

```

Q 3. In an experiment where we roll four dice:


```{r}
# Roll 4 dice

roll_4_dice <- rolldie(4)

total_roll_4_dice <- 
roll_4_dice %>%
nrow()

# how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)

roll_4_dice <- roll_4_dice %>%
  mutate(total = X1 + X2 + X3 + X4)


# total_equals_5

sum_equals_5 <- roll_4_dice %>%
  filter(total == 5)
 
total_equals_5 <- nrow(sum_equals_5)

# total_equals_6

sum_equals_6 <- roll_4_dice %>%
  filter(total == 6)
 
total_equals_6 <- nrow(sum_equals_6)

```

prob(event)=num(event outcomes)/num(all outcomes)

```{r}
# what is the probability of this event?

prob_equals_5 <- total_equals_5 / total_roll_4_dice

prob_equals_5


prob_equals_6 <- total_equals_6 / total_roll_4_dice

prob_equals_6

```

Q4 4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?






























