---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(ggplot2)
library(tidyverse)
library(CodeClanData)

```


Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.


```{r}

backpack <- backpack

```


```{r}
names(backpack)


```

Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.


```{r}

# distribution of backpack weight
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(bins = 20, col = "white", fill = "light blue") + 
  theme_light() + 
  labs(y = "number of backpacks", x = "weight")


```

Most are howevering between 5-15 backpack weights.

Question 3.

Are there differences in backpack weight between sex?


```{r}

# women or men carrying heavier backpacks?
ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  scale_fill_manual(values=c('#E69F00', '#56B4E9')) +
  geom_histogram(bins = 20, col = "white") + 
  theme_light() + 
  labs(y = "number of backpacks", x = "weight") + 
  facet_wrap(~sex)

```

Q4 What is the relationship between body weight and backpack weight?

```{r}
# relationship between weight and backpack weight?
ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight) + 
  geom_point() + 
  labs(x = "body weight", y = "backpack weight")


```

Q5 Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
# different for males vs females?
ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = sex) + 
  geom_point() + 
  facet_wrap(~sex) + 
    scale_color_manual(values=c('#E69F00', '#56B4E9'))+
    labs(x = "body weight", y = "backpack weight")


```

Q6 What proportion of students report back pain?

```{r}
# convert backpain to factor and create labelled column
backpack <- backpack %>%
  mutate(backpain_labelled = recode(back_problems, 
                       "0" = "No", 
                       "1" = "Yes"))

ggplot(backpack) + 
  aes(x = backpain_labelled, fill = backpain_labelled) + 
  geom_bar() +
ylim(0,100) + 
  labs(x = "backpain reported", y = "student count") +
    scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")

```

Q7 Is this proportion different between men and women?

```{r}
# is it different for males and females?
ggplot(backpack) + 
  aes(x = backpain_labelled, fill = backpain_labelled) + 
  geom_bar() +
  labs(x = "backpain reported", y = "student count") + 
  facet_wrap(~sex) +
      scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")


```


Q8 Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

```{r}
# make the labels nice
pain_labels <- c("backpain: no", "backpain: yes")
names(pain_labels) <- c("No", "Yes")

sex_labels <- c("sex: female", "sex: male")
names(sex_labels) <- c("Female", "Male")


ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = backpain_labelled) + 
  geom_point() + 
  facet_grid(sex ~ backpain_labelled, 
             labeller = labeller(backpain_labelled = pain_labels, sex = sex_labels)) + 
  labs(x = "\n body weight", y = "backpack weight \n") +
      scale_color_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")


```

























