---
title: "Advance ggplot"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
library(ggplot2)

```

```{r}

qb_revenue_breakdown <- qb_revenue_breakdown

```

Q1 Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
ggplot(qb_revenue_breakdown) +
 aes(fill = Product, y = Revenue, x = Year) + 
    geom_bar(stat="identity") +
   labs(y = "Total Revenue", x = "Year")
```


Q2 Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.

```{r}
qb_monthly_sales <- qb_monthly_sales

kwikBit_unit1 <- subset(qb_monthly_sales, Cashflow == "Kwikbit Unit 1 Sales")

```

```{r}
ggplot(kwikBit_unit1) +
  aes(x = Amount, color = Cashflow, y = Date) +
  geom_line()  +
  scale_color_brewer(palette = "Paired") 
  
  

```


Q3 Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}

monthly_rev <- subset(qb_monthly_sales, Cashflow == "Cost")

```

```{r}
# monthly revenue and costs over the last year. This data is also in qb_monthly_sales

ggplot(monthly_rev) +
  aes(x = Amount, color = Cashflow, y = Date) +
  geom_line() +
  scale_color_brewer(palette = "Paired") +
  labs(y = "Year", x = "Monthly sale")



```



Q4 Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
qb_competitors <- qb_competitors
options(scipen = 999)

```


```{r}

ggplot(qb_competitors) +
  aes(x = Year, color = Company, y = Revenue) +
  geom_area() +
  scale_color_brewer(palette = "Paired") +
  labs(x = "Year", y = "Annual sales")


```












